Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Fit figure width

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets. Content word overlap indicates a shared relationship among tweets. The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring."}

@@

```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion. Real-world events and linguistic cohesion continually interact and influence one another throughout time."}

@@

In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by
horizontal red lines, and the 99th percentiles are represented by horizontal
orange lines. The trend lines are plotted in blue.

>>>>

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets. Content word overlap indicates a shared relationship among tweets. The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}

@@

```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion. Real-world events and linguistic cohesion continually interact and influence one another throughout time.", out.width='100%'}

@@

In the WCRQA plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by
horizontal red lines, and the 99th percentiles are represented by horizontal
orange lines. The trend lines are plotted in blue.
